Results

### 2024-04-05 Sections/Intro.qmd
test toc
update
more toc testing

>>>>

---
code-fold: true
code-tools: true
toc: true
#toc-location: body
toc-title: Contents
---

[Link to HTW project page](https://tegorman13.github.io/htw/)\

[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html)

[repo](https://github.com/tegorman13/htw)
_______________________________________________________________________________

### 2024-04-05 Sections/Results.qmd
more toc testing

---
title: Results
author: "Thomas Gorman"
toc: true
toc-depth: 3
toc-expand: true
number-sections: true
number-depth: 5
strip-comments: true
cold-tools: true
echo: false
format: 
  html:
    column: 
      - screen-inset-right
  hugo-md:
    echo: false
    html-math-method: mathjax
    output-file: full-results-hugo.md
  # gfm:
  #   echo: true
  #   output-file: e1-gfm.md
#toc: true
# toc-title: Contents
# toc-depth: 4
# toc-expand: 1
# execute:
#   echo: false
---

>>>>

---
title: Results
author: "Thomas Gorman"
toc: true
# toc-depth: 3
# toc-expand: true
number-sections: true
number-depth: 5
strip-comments: true
cold-tools: true
echo: false
format: 
  html:
    column: 
      - screen-inset-right
  hugo-md:
    echo: false
    html-math-method: mathjax
    output-file: full-results-hugo.md
  # gfm:
  #   echo: true
  #   output-file: e1-gfm.md
#toc: true
# toc-title: Contents
# toc-depth: 4
# toc-expand: 1
# execute:
#   echo: false
---
